Journey: A Study in Unhelpful Titles (TODO: should we get a new title?)

### 2017-04-25 paper.tex
Moved to figures dir
Added email addresses to paper
assigned results section
Updated figures

\title{Journey: A Study in Unhelpful Titles (TODO: should we get a new title?)}
\author{Mark Mansi, Suhas Pai, Hasnain Ali Pirzada}
\date{}

@@

\begin{figure}
    \includegraphics[width=\columnwidth]{memory_controled}
    \caption{$\Delta_i$ adjusted with control for benchmarks}
\end{figure}

\begin{figure}
    \includegraphics[width=\columnwidth]{vm_area_struct_count}
    \caption{Number of \texttt{vm\_area\_struct}s for benchmarks}
\end{figure}

TODO: memory results

TODO: time results

@@

TODO

>>>>

\title{Journey: A Study in Unhelpful Titles (TODO: should we get a new title?)}
\author{Mark Mansi, Suhas Pai, Hasnain Ali Pirzada\\\texttt{\{markm, hp, spai\}@cs.wisc.edu}}
\date{}

@@

\begin{figure}
    \includegraphics[width=\columnwidth]{figures/mmap_mem_usage}
    \caption{$\Delta_i$ adjusted with control for benchmarks}
\end{figure}

\begin{figure}
    \includegraphics[width=\columnwidth]{figures/vm_area_struct_count}
    \caption{Number of \texttt{vm\_area\_struct}s for benchmarks}
\end{figure}

TODO: memory results: SPAI

TODO: time results: HP

@@

TODO: memory: SPAI

TODO: time: HP/MARKM

\begin{figure}
    \includegraphics[width=\columnwidth]{figures/swap_touch_time_cont_cdf}
    \caption{CDF Time to touch a page while swapping for continuous benchmark}
\end{figure}
\begin{figure}
    \includegraphics[width=\columnwidth]{figures/swap_touch_time_rand_cdf}
    \caption{CDF Time to touch a page while swapping for random benchmark}
\end{figure}

TODO: time: MARKM
